---
title: "2018/2020 water Quality Report and list of Water Quality Limited Waters"
subtitle: "Response to Public Comments"
output:
  word_document:
    reference_docx: Report_Template.docx
    toc: TRUE
    fig_caption: true
always_allow_html: yes
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning=FALSE,
                      error = TRUE,
                      cache = FALSE,
                      cache.comments = FALSE,
                      include = TRUE,
                      autodep = TRUE,
                      fig.height = 6,
                      eval = TRUE
                      )

library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(kableExtra)
library(captioner)

tbls  <- captioner(prefix="Table")

```

```{r inputs}

# Needs to run from local directory
#setwd("E:/GitHub/RTC/")

sc.xlsx <- "suggested_changes.xlsx"

sc.cols <- c("Comment_Number", "Title", "Comment", "Response", "Response_Type", "Assigned_To", "Status", 
             "Action_Needed", "Rule_Change", "Commenter","Num_Comments","Num_Commenters", "ID", "Comment_Text","Notes")  

sc.col.type <- c("numeric","text","text","text","text","text","text",
                 "text","logical","text","numeric","numeric","numeric","text","text")


cm.xlsx <- "comments.xlsx"

cm.cols <- c("Commenter","Comment_Period","DASID","First_Name","Last_Name","Email","Organization",
             "State","Comment_Text","Attachment_Name", "Attachment_URL", "CARA.URL", "Manually_Entered", "Num_Commenters", 
             "Summary", "Status","Notes","Comment_Number", "ID")

cm.col.type <- c("numeric","text","numeric","text","text","text","text",
                 "text","text","text","text","text","logical", "numeric",
                 "text","text","text","text", "numeric")

df.sc1 <- read_excel(sc.xlsx, col_names = sc.cols, skip=1, col_types = sc.col.type, na=c(""), trim_ws=TRUE)
df.cm1 <- read_excel(cm.xlsx, col_names = cm.cols, skip=1, col_types = cm.col.type, na=c(""), trim_ws=TRUE)

df.cm2 <- df.cm1 %>%
  dplyr::mutate(Organization = ifelse(is.na(Organization), paste(First_Name, Last_Name),Organization )) %>%
  dplyr::select(Commenter, Organization) %>%
  dplyr::mutate(Org_Acronym=str_replace_all(Organization, c("the"="",
                                                   "of"="",
                                                   "and"="-"))) %>%
  dplyr::mutate(Org_Acronym=abbreviate(Org_Acronym, use.classes = TRUE, minlength=2, dot=FALSE))%>%
  dplyr::mutate(Org_Acronym=gsub("USDIBR","BOR",Org_Acronym)) %>%
  dplyr::mutate(Org_Acronym = make.unique(Org_Acronym, sep = "."))

df.sc2 <- df.sc1 %>%
  dplyr::select(Comment_Number, Title, Comment, Response, Commenter, ID) %>%
  separate_rows(Commenter, sep = ", ", convert=TRUE) %>%
  dplyr::left_join(df.cm2,by="Commenter") %>%
  dplyr::arrange(Commenter, ID)


n.cm <- nrow(df.cm2)

n.sc <- nrow(df.sc1)

# Does not check for any NAs or suggested changes that still need to be made.
n.tmdl.mods <- df.sc1 %>%
  dplyr::filter(Response_Type=="Yes, changes were made to TMDL/WQMP") %>%
  nrow()

```

# Introduction

This Response to Public Commetns document addresses comments and questions received regarding the Draft Draft 2018/2020 Water Quality Report and List of Water Quality Limited Waters (2018/2020 Integrated Report).  The individuals and organizations shown in `r tbls(name='tbl.commenters', display='cite')` provided comments on the 2018/2020 Integgrated Report during the Public Comment Period which was held from September 30, 2019 through January 6, 2020.  All comments received during the public comment period have been reviewed by DEQ and addressed in this document. Comments which required modifications to the report are noted. In total there were `r n.sc` unique comments from `r n.cm` entities. DEQ made modifications to the report based on `r n.tmdl.mods` of the comments

```{r commenters-table1, results = 'asis'}

knitr::kable(df.cm2, format = "pandoc", padding = 2, digits = 1,
             col.names = c("Commenter #", "Commenter", "Acronym"),
             caption = tbls(name="tbl.commenters",
                            caption="Commenters on the May 2019 Draft Upper Klamath and Lost Subbasins Temperature TMDL and WQMP."))

```


```{r Comments-Responses, results = 'asis'}

for(i in 1:nrow(df.cm2)) {
  
  commenter_name <- df.cm2[i,"Organization", drop=TRUE ]
  commenter_acronym <- df.cm2[i,"Org_Acronym", drop=TRUE]
  
  cat(paste("# Comments from: ",commenter_name))
  cat(" \n\n")
  
  df.sc2.i <- df.sc2 %>%
    dplyr::filter(Org_Acronym==commenter_acronym)

  for(row in 1:nrow(df.sc2.i)){
    
    comment_number <- df.sc2.i[row,"Comment_Number", drop=TRUE]
    comment_title <- df.sc2.i[row,"Title", drop=TRUE]
    comment <- df.sc2.i[row,"Comment", drop=TRUE]
    response <- df.sc2.i[row,"Response", drop=TRUE]
    
    cat(paste0(commenter_acronym,"#",row,": Suggested Change ID #",comment_number," \n\n"))
    cat(paste0("**Description: ",comment_title,"** \n\n"))
    cat(paste0("**Comment:** ",comment," \n\n"))
    cat(paste0("**Response:**  ",response," \n\n"))
    cat("---")
    cat(" \n\n")
  }
  
}

```
